Advice on describing Bayesian analysis of neutron and X-ray reflectometry

### 2022-07-21 src/tex/ms.tex
Add Zenodo reference

Either the full posterior chain or the thinned chain should be shared along with details of any autocorrelation analysis to accompany any Bayesian or sampling analysis. 
This will allow the best replication and verification of any results obtained from the data. 
Furthermore, large output files such as these chains can be easily shared using some versioned data repository, such as Zenodo or those available at specific institutions. 
Additionally, to allow the reader to quickly interpret the sampled posterior, a graphical description (such as that in Figure~\ref{fig:post}) should be included, at a minimum, in the supplementary information of the work. 
The importance of presenting the full posterior graphically lies in the ability to easily interpret correlations between parameters through this medium.
For example, in Figure 3, the ellipsoidal probability distribution (for the d/rho) parameters indicates correlation.
%
\begin{figure}
  \script{post.py}
  \includegraphics[width=\columnwidth]{figures/post.pdf}
  \caption{
    An example of a graphical depiction of the unthinned posterior as a corner plot (produced using the \texttt{corner.py} package \cite{foremanmackey_corner_2016}), representing a three-dimensional probability distribution showing the posterior distribution for the parameters of nickel magnetic scattering length density, nickel mass density, and nickel layer thickness, from the analysis of a nickel layer on a silicon block.
  }
  \label{fig:post}
\end{figure}
%

>>>>

Either the full posterior chain or the thinned chain should be shared along with details of any autocorrelation analysis to accompany any Bayesian or sampling analysis. 
This will allow the best replication and verification of any results obtained from the data. 
Furthermore, large output files such as these chains can be easily shared using some versioned data repository, such as Zenodo \cite{european_zenodo_2013} or those available at specific institutions. 
Additionally, to allow the reader to quickly interpret the sampled posterior, a graphical description (such as that in Figure~\ref{fig:post}) should be included, at a minimum, in the supplementary information of the work. 
The importance of presenting the full posterior graphically lies in the ability to easily interpret correlations between parameters through this medium.
For example, in Figure 3, the ellipsoidal probability distribution (for the d/rho) parameters indicates correlation.
%
\begin{figure}
  \script{post.py}
  \includegraphics[width=\columnwidth]{figures/post.pdf}
  \caption{
    An example of a graphical depiction of the unthinned posterior as a corner plot (produced using the \texttt{corner.py} package \cite{foremanmackey_corner_2016}), representing a three-dimensional probability distribution showing the posterior distribution for the parameters of nickel magnetic scattering length density, nickel mass density, and nickel layer thickness, from the analysis of a nickel layer on a silicon block.
  }
  \label{fig:post}
\end{figure}
%
